\papertitle

### 2017-07-21 article-icmc2017.tex
wip

\node (t1) at (1.45, -3.45) {\footnotesize $t_0$};
\node (t2) at (4, -3.45) {\footnotesize $t_1$};
\node (t3) at (6.5, -3.45) {\footnotesize $t_2$};
\end{tikzpicture}
\caption{Another execution trace, stemming from a different score than the one presented in fig.~\ref{fig.tgraph}. $f_2$'s input corresponds to $f_1$'s output, delayed: this creates a causality problem. }
\label{fig.delay}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{tikzpicture}[scale=0.45]
	\draw[] (0, 0) rectangle (4, 2) node[pos=.5] { $f_1$ };
	\draw[] (1, -2.5) rectangle (2, -0.5) node[pos=.5] { $f_2$ };
	\draw[] (3.5, -2.5) rectangle (4.5, -0.5) node[pos=.5] { $f_3$ };
	\draw[] (6, -2.5) rectangle (7, -0.5) node[pos=.5] { $f_4$ };

	\end{tikzpicture}
	\caption{$f_2$, $f_3$ and $f_4$ read from $f_1$ with a delayed connection.}
	\label{fig.delay2}
\end{figure}

@@

The C++ implementation of the execution algorithm itself, provided in the OSSIA library is not tied in any way to PureData or any other environment: PureData is used as an example of implementation of a node to leverage an easy and well-known method to produce generators and filters with different kinds of inputs and outputs, which allows to cover the whole set of features.
Other nodes can be implemented through inheritance of a set of C++ classes.
As such, the processes currently available in i-score (automations, Javascript code, MIDI piano roll) and in i-score-audio (sound file reading, Faust and LV2 effects) are being ported to this new execution model.

@@

    \caption{The dataflow relationships between instances of $f_{1,..5}$ in the program. The global environment contains variables for \lstinline|/vol| and \lstinline|/filt| when the execution starts.}
    \label{fig.datapatch}
\end{figure}~
\begin{figure}
    \centering
    \begin{tikzpicture}
    \input{scores/score2.tex}
    \end{tikzpicture}
    \caption{The temporal relationships between instances of $f_{1,..5}$ in the program.}
    \label{fig.timepatch}
\end{figure}

>>>>

\node (t1) at (1.45, -3.45) {\footnotesize $t_0$};
\node (t2) at (4, -3.45) {\footnotesize $t_1$};
\node (t3) at (6.5, -3.45) {\footnotesize $t_2$};
\end{tikzpicture}
\caption{Another execution trace, stemming from a different score than the one presented in fig.~\ref{fig.tgraph}. $f_2$'s input corresponds to $f_1$'s output, delayed: this creates a causality problem. }
\label{fig.delay}
\end{figure}\vspace{-5mm}
\begin{figure}[h]
	\centering
	\begin{tikzpicture}[scale=0.45]
	\draw[] (0, 0) rectangle (4, 2) node[pos=.5] { $f_1$ };
	\draw[] (1, -2.5) rectangle (2, -0.5) node[pos=.5] { $f_2$ };
	\draw[] (3.5, -2.5) rectangle (4.5, -0.5) node[pos=.5] { $f_3$ };
	\draw[] (6, -2.5) rectangle (7, -0.5) node[pos=.5] { $f_4$ };

	\end{tikzpicture}
	\caption{$f_2$, $f_3$ and $f_4$ read from $f_1$ with a delayed connection.}
	\label{fig.delay2}
\end{figure}
\vspace{-5mm}

@@

The C++ implementation of the execution algorithm, provided in the OSSIA library, is not tied in any way to PureData or any other environment: PureData is used as an example of implementation of a node to leverage an easy and well-known method to produce generators and filters with different kinds of inputs and outputs, which allows to cover the whole set of features.
Other nodes can be implemented through inheritance of a set of C++ classes.
As such, the processes currently available in i-score (automations, Javascript code, MIDI piano roll) and in i-score-audio (sound file reading, Faust and LV2 effects) are being ported to this new execution model.

@@

    \caption{The dataflow relationships between instances of $f_{1,..5}$ in the program. The global environment contains variables for \lstinline|/vol| and \lstinline|/filt| when the execution starts. A PureData patch with similar semantics would use additionally \lstinline|throw~, catch~, send, receive, delwrite~, delread~,tabwrite~, tabread~| between nodes, and UDP \& OSC receivers and senders to read and write from the environment.}
    \label{fig.datapatch}
\end{figure}~
\begin{figure}
    \centering
    \begin{tikzpicture}
    \input{scores/score2.tex}
    \end{tikzpicture}
    \caption{The temporal relationships between instances of $f_{1,..5}$ in the program.}
    \label{fig.timepatch}
\end{figure}
